### 2021-04-22 [2020-08]_ACMTOMS_(MQSI)/paper/1-introduction.tex

The currently available software for monotone piecewise polynomial
interpolation includes quadratic [He and Shi 1998, McAllister and
Roulier 1981], cubic [Fritsch and Carlson 1980], and (with limited
application) quartic [Wang and Tan 2004; Piah and Unsworth 2011; Yao
and Nelson 2018] cases. In addition, a statistical method for
bootstrapping the construction of an arbitrarily smooth monotone fit
exists [Leitenstorfer and Tutz 2006], but the method does not take
advantage of known analytic properties of quintic polynomials.
Conversely the work on quadratic shape preserving splines by Schumaker
[1983] is widely utilized in theory for its conservation of both
monotonicity and convexity, but a mathematical software is not readily
available.

>>>>

The currently available software for monotone piecewise polynomial
interpolation includes quadratic [He and Shi 1998, McAllister and
Roulier 1981], cubic [Fritsch and Carlson 1980], and (with limited
application) quartic [Wang and Tan 2004; Piah and Unsworth 2011; Yao
and Nelson 2018] cases. In addition, a statistical method for
bootstrapping the construction of an arbitrarily smooth monotone fit
exists [Leitenstorfer and Tutz 2006], but the method does not take
advantage of known analytic properties of quintic polynomials.
Conversely the work on quadratic shape preserving splines by Schumaker
[1983] is widely utilized in theory for its conservation of both
monotonicity and convexity, but no mathematical software is published.

### 2021-04-22 [2020-08]_ACMTOMS_(MQSI)/paper/5-applications.tex

>>>>

Comparisons between this work and lower order methods are problematic,
especially with sparse data. For exact data from smooth functions,
comparing derivative values, higher order methods always win (all
other things being equal) as the data density increases. For sparse or
synthetic data, what constitutes a better fit is either subjective or
dependent on the specific problem. If an application demands $C^2$
continuity and monotonicity, the target of {\tt MQSI}, then this
package provides such interpolants while no existing published spline
software suffices.

### 2021-04-22 [2020-08]_ACMTOMS_(MQSI)/paper/mqsi20.tex
Final modifications to ACM TOMS paper before submission.
Initial response to TOMS editor.

% Algorithm XXXX: MQSI---Monotone quintic spline interpolation,
% Thomas C.H. Lux, Layne T. Watson, Tyler H. Chang,
% and William Thacker
% ACM Trans. Math. Software, ?/?/2020.
% 
%
\magnification=1000 \hsize=30pc \vsize=47pc
\parindent=10pt \parskip=0pt plus 3pt
\baselineskip=13pt plus 2pt minus 1pt \lineskiplimit=2pt
\lineskip=2pt plus 2pt %\raggedright
\tolerance=800
%\abovedisplayskip=6pt plus 6pt minus 3pt
%\abovedisplayshortskip=0pt plus 3pt
%\belowdisplayskip=6pt plus 6pt minus 3pt
%\belowdisplayshortskip=6pt plus 2pt minus 3pt

@@

@@

@@

>>>>

% Algorithm XXXX: MQSI---Monotone quintic spline interpolation,
% Thomas C.H. Lux, Layne T. Watson, Tyler H. Chang,
% and William Thacker
% ACM Trans. Math. Software, ?/?/202?.
% 
%
\magnification=1000 \hsize=30pc \vsize=47pc
\parindent=10pt \parskip=0pt plus 3pt
\baselineskip=13pt plus 2pt minus 1pt \lineskiplimit=2pt
\lineskip=2pt plus 2pt %\raggedright
\tolerance=800
%\abovedisplayskip=6pt plus 6pt minus 3pt
%\abovedisplayshortskip=0pt plus 3pt
%\belowdisplayskip=6pt plus 6pt minus 3pt
%\belowdisplayshortskip=6pt plus 2pt minus 3pt

@@

%% 10002950.10003705
%% Mathematics of computing~Mathematical software
%% 
%% 10002950.10003648.10003649.10003657.10003659
%% Mathematics of computing~Spline models
%% 
%% 10002950.10003714.10003715.10003722
%% Mathematics of computing~Interpolation
%% 
%% 10002950.10003714.10003715
%% Mathematics of computing~Numerical analysis
%% 
%% 10002950.10003648.10003649.10003657
%% Mathematics of computing~Nonparametric representations

@@

% mcallister1981algorithm
\refj{McAllister, D. F. and Roulier, J. A.}{1981}{An algorithm for 
  computing a shape-preserving osculatory quadratic spline}{ACM 
  Transactions on Mathematical Software (TOMS)}{7(3):331--347}

% mcallister1981shape
\refj{McAllister, D. F. and Roulier, J. A.}{1981}{Algorithm 574:
  Shape-Preserving Osculatory Quadratic Splines [E1, E2]}{ACM
  Transactions on Mathematical Software (TOMS)}{7(3):384--386}

% moler2004numerical
\refb{Moler, C. B.}{2008}{Numerical Computing with {\caps Matlab}}{
  The MathWorks Inc., Natick, Massachusetts}

@@

% schumaker1983shape
\refj{Schumaker, Larry L.}{1983}{On shape preserving quadratic spline
  interpolation}{SIAM Journal on Numerical Analysis}{20(4):854--864}
